Matching Bullets

### 2015-12-02 imaging-paper.Rnw
bullet-stats and crosscuts are dependent on previous version of xpr3plus

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Loess fit residuals for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess <- fit_loess(br111_bullet, br111.groove)

@@

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=3) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=1) + ggtitle("Land 1 of Bullet 1 in black")
@    
\caption{Residuals of a loess fit to bullets 1 and 2 from barrel 1. Land 1 of bullet 1 is shown in black. }
\end{figure}

>>>>

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Residuals of Loess fit for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess <- fit_loess(br111_bullet, br111.groove)

@@

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=1) + ggtitle("Land 1 of Bullet 1 in black")
@    
\caption{Residuals of a loess fit to bullets 1 and 2 from barrel 1. Land 1 of bullet 1 is shown in black. }
\end{figure}
